Model Checking Differentially Private Properties

### 2018-01-30 introduction.tex
contributions

>>>>

\paragraph{Contributions.} Our main contributions are three folds. (i)
We introduce the logic $\dpCTLstar$ for reasoning about properties in 
differential privacy. We use the logic to express classical
differential privacy properties, and moreover, complex properties such as those 
involving infinite behaviors can also be expressed. (ii) We model several differential privacy mechanisms, including the streaming process, in Markov chains or MDPs.
(iii) We show that the model checking problem 
problem for Markov chains is standard. For MDPs we show that it is undecidable.
